Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-18 paper/main.tex
homolog -> bilateral
I think this better describes what we intent to say

% AV intro
First, we analyzed data from the movie offering a visual but ecologically more
valid stimulation than static pictures.
% AV primary contrast
The movie's primary $t$-contrast that compared cuts to a setting that was not
depicted before to cuts within a recurring setting (\texttt{vse\_new >
vpe\_old}) yielded three significant clusters (Tab.~\ref{tab:res-av-group1},
Fig.~\ref{fig:group-slices}).
% PPA (others the clusters extend into).
One cluster spans across the midline and comprises parts of the intracalcarine
and cuneal cortex, the lingual gyrus and retrosplenial cortex, the occipital and
temporal fusiform gyrus, and the parahippocampal cortex (reported from posterior
to anterior) in both hemispheres.
% LOC
Two additional homologous clusters are located in the superior lateral occipital
cortex.

% AD intro
Second, we analyzed data from the audio-description offering exclusively
auditory stimulation.
% AD primary contrast
The primary $t$-contrast for the audio-description (\texttt{geo, groom} >
non-spatial noun categories) yielded six significant clusters
(Tab.~\ref{tab:res-ao-group1}, Fig.~\ref{fig:group-slices}).
% overlap with ROI
Two homologous clusters are located in the anterior part of the PPA group
overlap reported by \cite{sengupta2016extension}.
% in detail
Specifically, these clusters are located at the borders of the posterior
parahippocampal cortex, the occipital and temporal fusiform gyrus and lingual
gyrus.
% precuneus
Two additional homologous clusters are apparent in the ventral precuneus
extending into the retrosplenial cortex.
% LOC
Finally, two homologous clusters are located in the superior lateral occipital
cortex.

>>>>

% AV intro
First, we analyzed data from the movie offering a visual but ecologically more
valid stimulation than static pictures.
% AV primary contrast
The movie's primary $t$-contrast that compared cuts to a setting that was not
depicted before to cuts within a recurring setting (\texttt{vse\_new >
vpe\_old}) yielded three significant clusters (Tab.~\ref{tab:res-av-group1},
Fig.~\ref{fig:group-slices}).
% PPA (others the clusters extend into).
One cluster spans across the midline and comprises parts of the intracalcarine
and cuneal cortex, the lingual gyrus and retrosplenial cortex, the occipital and
temporal fusiform gyrus, and the parahippocampal cortex (reported from posterior
to anterior) in both hemispheres.
% LOC
Two additional bilateral clusters are located in the superior lateral occipital
cortex.

% AD intro
Second, we analyzed data from the audio-description offering exclusively
auditory stimulation.
% AD primary contrast
The primary $t$-contrast for the audio-description (\texttt{geo, groom} >
non-spatial noun categories) yielded six significant clusters
(Tab.~\ref{tab:res-ao-group1}, Fig.~\ref{fig:group-slices}).
% overlap with ROI
Two bilateral clusters are located in the anterior part of the PPA group
overlap reported by \cite{sengupta2016extension}.
% in detail
Specifically, these clusters are located at the borders of the posterior
parahippocampal cortex, the occipital and temporal fusiform gyrus and lingual
gyrus.
% precuneus
Two additional bilateral clusters are apparent in the ventral precuneus
extending into the retrosplenial cortex.
% LOC
Finally, two bilateral clusters are located in the superior lateral occipital
cortex.
